The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multi-Phase Forest Inventories

### 2017-09-07 rnw/Threephase_Estimators and their Application.Rnw
update Andreas 07.09.2017(3)

\begin{small}
<<>>=
reg2p_nex<- twophase(formula = formula.rm, data = grisons,
                       phase_id = list(phase.col="phase_id_3p", terrgrid.id = 2),
                       boundary_weights = "boundary_weights")
@
\end{small}

>>>>

\begin{small}
<<>>=
reg2p_nex<- twophase(formula = formula.rm, data = grisons,
                       phase_id = list(phase.col="phase_id_2p", terrgrid.id = 2),
                       boundary_weights = "boundary_weights")
@
\end{small}
